Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Typos

\subsubsection{Single-Step Transition}
Before describing how the machine evaluates expressions, we must first define several helper
functions. As mentioned in Section~\ref{anfsyntax}, atomic expressions are either a variable
or a literal @lambda@ term. As such, the atomic expression evaluator @atomicEval@ handles
these two cases and evaluates atomic expressions to closures in a straightforward way.
The @alloc@ function generates a fresh address, and always allocates unique integer
in the domain of store.
The @isAtomic@ function is used as a predicate to determine if the expression is atomic.

@@

Now, we can faithfully describe the state transition function @step@,
that, when given a machine state, determines its successor state.

@@

In the first case, the control of current state is a @Let@ expression,
and its right-hand side is an function application.
By calling evaluator @atomicEval@, we obtain the closure that callee @f@ stands for.
The successor state's control then transfers to the @body@ expression of closure,
with an updated environment and an update store. The new environment is extended
from closure's environment and mapped @v@ to a fresh address @addr@.
The new store is extended with @addr@ mapping to the value of @ae@,
which is evaluated from @atomicEval@.
In the meanwhile, a new frame @frame@ is pushed onto the stack @k@.
This @frame@ contains the variable name @x@ at left-hand side position of @Let@,
the body expression of @Let@, and the lexical environment of the body expression.

>>>>

\subsubsection{Single-Step Transition}
Before describing how the machine evaluates expressions, we must first define several helper
functions. As mentioned in Section~\ref{anfsyntax}, atomic expressions are either a variable
or a literal @lambda@ term. As such, the atomic expression evaluator @atomicEval@ handles
these two cases and evaluates atomic expressions to closures in a straightforward way.
The @alloc@ function generates a fresh address, and always allocates a unique integer
in the domain of @store@.
The @isAtomic@ function is used as a predicate to determine if the expression is atomic.

@@

We can now faithfully describe the state transition function @step@,
which when given a machine state, determines its successor state.

@@

In the first case, the control of current state is a @Let@ expression,
and its right-hand side is a function application.
By calling the @atomicEval@ evaluator, we obtain the closure for which the callee @f@ stands.
The successor state's control then transfers to the @body@ expression of closure,
with an updated environment and an update store. The new environment is extended
from closure's environment and mapped @v@ to a fresh address @addr@.
The new store is extended with @addr@ mapping to the value of @ae@,
which is evaluated from @atomicEval@.
In the meanwhile, a new frame @frame@ is pushed onto the stack @k@.
This @frame@ contains the variable name @x@ at left-hand side position of @Let@,
the body expression of @Let@, and the lexical environment of the body expression.
